---
title: | 
  | Assignment 4: Collaborating Together
  | Introduction to Applied Data Science
  | 2022-2023
author: |
  | Dante Westerlaken
  | D.V.westerlaken@student.uu.nl
  | https://github.com/DanteWes
date: April 2023
urlcolor: purple
linkcolor: purple
output: 
  pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, error=TRUE)
```

## Assignment 4: Collaborating Together 

### Part 1: Contributing to another student's Github repository

In this assignment, you will create a Github repository, containing this document and the .pdf output, which analyzes a dataset individually using some of the tools we have developed. 

This time, make sure to not only put your name and student e-mail in your Rmarkdown header, but also your Github account, as I have done myself. 

However, you will also pair up with a class mate and contribute to each others' Github repository. Each student is supposed to contribute to another student's work by writing a short interpretation of 1 or 2 sentences at the designated place (this place is marked with **designated place**) in the other student's assignment. 

This interpretation will not be graded, but a Github shows the contributors to a certain repository. This way, we can see whether you have contributed to a repository of a class mate. 

**Question 1.1**: Fill in the __github username__ of the class mate to whose repository you have contributed. 

[Fill in here]

### Part 2: Analyzing various linear models

In this part, we will summarize a dataset and create a couple of customized tables. Then, we will compare a couple of linear models to each other, and see which linear model fits the data the best, and yields the most interesting results.

We will use a dataset called `GrowthSW` from the `AER` package. This is a dataset containing 65 observations on 6 variables and investigates the determinants of economic growth. First, we will try to summarize the data using the `modelsummary` package. 

```{r, warning=FALSE, message=FALSE}
library(AER)
data(GrowthSW)
```

One of the variables in the dataset is `revolutions`, the number of revolutions, insurrections and coup d'etats in country $i$ from 1965 to 1995.

**Question 2.1**: Using the function `datasummary`, summarize the mean, median, sd, min, and max of the variables `growth`, and `rgdp60` between two groups: countries with `revolutions` equal to 0, and countries with more than 0 revolutions. Call this variable `treat`. Make sure to also write the resulting data set to memory. Hint: you can check some examples [here](https://vincentarelbundock.github.io/modelsummary/articles/datasummary.html#datasummary).

```{r}


library(modelsummary); library(tidyverse)

# write your code here

data <- GrowthSW %>%
  mutate(treat = ifelse(revolutions > 0, "More than 0 Revolutions", "0 Revolutions"))

data

data_sum <- datasummary(growth + rgdp60 ~ treat*(mean + median + sd + min + max)  ,
            data = data)
data_sum

```

**Designated place**: type one or two sentences describing this table of a fellow student below. For example, comment on the mean and median growth of both groups. Then stage, commit and push it to their github repository. 


### Part 3: Make a table summarizing reressions using modelsummary and kable

In question 2, we have seen that growth rates differ markedly between countries that experienced at least one revolution/episode of political stability and countries that did not. 

**Question 3.1**: Try to make this more precise this by performing a t-test on the variable growth according to the group variable you have created in the previous question. 

```{r}
# write t test here

group1 <- data$growth[data$revolutions == 0]     
group2 <- data$growth[data$revolutions > 0]      


result <- t.test(group1, group2)


print(result)


```

**Question 3.2**: What is the $p$-value of the test, and what does that mean? Write down your answer below.


The p-value is in this case 0.06871. It tell you the likelihood that the null-hypothesis is true. Most of the time you accept the null-hupothesis when 0.05 <= P-value. In our case it is safe to say that we accept the null-hypothesis. 

We can also control for other factors by including them in a linear model, for example:

$$
\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \beta_2 \cdot \text{rgdp60}_i + \beta_3 \cdot \text{tradeshare}_i + \beta_4 \cdot \text{education}_i + \epsilon_i
$$

**Question 3.3**: What do you think the purpose of including the variable `rgdp60` is? Look at `?GrowthSW` to find out what the variables mean. 

rgdp60 is the value of GDP per capita in 1960, converted to 1960 US dollars. This variable can be used as a comprising to see how other have grown



We now want to estimate a stepwise model. Stepwise means that we first estimate a univariate regression $\text{growth}_i = \beta_0 + \beta_1 \cdot \text{treat}_i + \epsilon_i$, and in each subsequent model, we add one control variable. 

**Question 3.4**: Write four models, titled `model1`, `model2`, `model3`, `model4` (using the `lm` function) to memory. Hint: you can also use the `update` function to add variables to an already existing specification.

```{r}


model1 <- lm(data$growth ~ data$treat)

model2 <- update(model1, . ~ . + data$rgdp60)

model3 <- update(model2, . ~ . + data$tradeshare)

model4 <- update(model3, . ~ . + data$education)





```

Now, we put the models in a list, and see what `modelsummary` gives us:

```{r}
list(model1, model2, model3, model4) |>
  modelsummary(stars=T,
# edit this to remove the statistics other than R-squared
# and N 
gof_map = c("nobs", "r.squared")
) 


```

**Question 3.5**: Edit the code chunk above to remove many statistics from the table, but keep only the number of observations $N$, and the $R^2$ statistic. 

**Question 3.6**: According to this analysis, what is the main driver of economic growth? Why?

We can see that trade-share is de main driver of economic growth, because in model 4 where all the variable are included, you see that trade share has the highest value(1.813).

**Question 3.7**: In the code chunk below, edit the table such that the cells (including standard errors) corresponding to the variable `treat` have a red background and white text. Make sure to load the `kableExtra` library beforehand.

```{r}

library(kableExtra)

table <- list(model1, model2, model3, model4) |>
  modelsummary(stars=T, gof_map = c("nobs", "r.squared"))

table <- table %>%
  kable_styling() %>% row_spec(3, bold = TRUE, background = "red", color = "white")

table



```

**Question 3.8**: Write a piece of code that exports this table (without the formatting) to a Word document. 

```{r}
library(kableExtra)
library(officer)

# Create the table
table <- list(model1, model2, model3, model4) %>%
  modelsummary(stars = TRUE, gof_map = c("nobs", "r.squared")) %>%
  kable()

# Convert the table to a data frame
table_df <- as.data.frame(table)

# Create a Word document
doc <- read_docx()

# Add the table to the document
doc <- body_add_table(doc, table_df)

# Save the document
output_file <- "table_output.docx"
print(doc, target = output_file)



```

## The End
